Running an open experiment: transparency and reproducibility in soil and ecosystem

### 2016-02-04 manuscript_methods/Open_experiment.Rmd
Added Nosek and Lewandowsky refs

@@

>>>>

Pushing scientists towards "best practices" in dealing with data and code {Hart, 2015 #4292;Wilson, 2014 #4337}.

@@

Transparency is no magic panacea ensuring reproducibility {Easterbrook, 2014 #4137}, and it raises genuine concerns about, for example, protecting scientists from harassment {Lewandowsky, 2016 #4342}. We also recognize that our professional and career incentives do not yet align well with "an open research culture" {Nosek, 2015 #4343}.
